---
title: "Analysis script"
author: "Linh Nguyen"
date: "05/05/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Meta-Data

```{r, message = F, warning = F}
require(tidyverse)
require(rio)
require(summarytools)
require(psych)
require(metafor)
set.seed(202104)
sessionInfo()
```

## Data prepping

### Read in data

This dataset includes the full-text coding of the first 30 eligible articles during the pilot stage with 34 samples. None of these articles reported the needed statistics, so these values will be simulated in the next section. Only personality at the Big Five level (OCEAN traits) are included. Some descriptive statistics of study characteristics are presented below:

```{r, message = F, warning = F, results = "asis"}
#read in the needed columns
data <- rio::import("Coding-2021-04-23.xlsx") %>% 
  select(-c(PDF, Year, Author, Title, Journal, Vol, Issue, Pages, Location, Notes, Archival))

#number of samples
data <- data %>% 
  mutate(ID = ifelse(is.na(Study), ID,
                     paste0(ID, "_", Study)))

#reasons for ineligibility 
data %>% group_by(Eligible) %>% 
  summarise(n = n())%>% 
  knitr::kable()
data %>% filter(Eligible == "No") %>% 
  group_by(Why_ineligible) %>%
  summarise(reason = n()) %>% 
  knitr::kable()

#remove ineligible studies
data <- data %>% 
  filter(Eligible != "No")

#clean-up descriptives
data$N <- as.numeric(data$N)

data[which(data$MAge == "49.8 (M) and 45.5 (F)"),]$MAge <- (49.8+45.5)/2
data[which(data$SDAge == "17.3 (M) and 14.1 (F)"),]$SDAge <- (17.3+14.1)/2
data$MAge <- round(as.numeric(data$MAge), digits = 3)
data$SDAge <- round(as.numeric(data$SDAge), digits = 3)
data[which(as.numeric(data$White) > 1),]$White <- as.numeric(data[which(as.numeric(data$White) > 1),]$White)/100
data$Fem <- round(as.numeric(data$Fem), digits = 3)
data$White <- round(as.numeric(data$White), digits = 3)

data$num = 1
for (i in 1:(length(data$ID)-1)){
  data[i,]$num <- ifelse(data[i,]$ID != data[i+1,]$ID, 1, NA)
}

descr <- data %>% filter(num == 1) %>% select(N,MAge, SDAge, Fem, White)
descr(descr, stats = "common", order = "p")

#pool ESM + DD = ESM
data <- data %>% 
  mutate(Design = ifelse(Design == "DD", "ESM", Design))

#emotion variable with two levels (positive and negative)
data <- data %>% 
  mutate(EmoPN = ifelse(str_detect(Emo, "Positive") | str_detect(Emo, "Happ") |
                          str_detect(Emo, "Authenticity"), "Positive",
                        ifelse(str_detect(Emo, "Negative") | str_detect(Emo, "stress") | 
                                 str_detect(Emo, "distress") | str_detect(Emo, "boredom")|
                                 str_detect(Emo, "sadness") | str_detect(Emo, "strain") |
                                 str_detect(Emo, "Anxiety") | str_detect(Emo, "Stress") |
                                 str_detect(Emo, "Depression") | str_detect(Emo, "Burnout") |
                                 str_detect(Emo, "Powerlessness"), "Negative", NA)))

#only select big five domains (OCEAN)
pers <- c("Agreeableness", "Conscientiousness", "Extraversion", "Neuroticism", "Openness")
data <- data %>% 
  filter(Pers %in% pers)
data %>% 
  group_by(Pers) %>% 
  summarise(n = n())%>% 
  knitr::kable()
freq(data$Pers)
freq(data$ID)
freq(data$Design)
```

### Simulate correlation

```{r}
#sample from normal distribution (fisher's z, mean = 0.1, sd = 0.2) 
data$Corr <- rnorm(n = nrow(data), mean = 0.1, sd = 0.2)

#transformed to pearson's correlation
data$Corr <- fisherz2r(data$Corr)
hist(data$Corr)
```

## Data analysis

```{r}
#compute sampling sampling variances `vi`
data <- escalc(measure = "COR",
               ri = Corr,
               ni = N, 
               data = data,
               slab = ID) %>% select(-yi)
```

### Neuroticism and variability in Emotions

Analyses are run separately for each personality trait. For ease of presentation, only the model for Neuroticism is shown here:

```{r, fig.width = 7, fig.height = 10}
neuroticism <- rma.mv(yi = Corr,
                      V = vi,
                      data = data[which(data$Pers == "Neuroticism" & !is.na(data$EmoPN)),],
                      method = "REML",
                      level = 95, 
                      digits = 4,
                      slab = ID,
                      random = ~1 | ID)
neuroticism

par(mar=c(2.5,4,1,2.5), cex = .9, font = 1)

forest(neuroticism,
       xlim = c(-2,2),
       order = "obs",
       addfit = T,
       annotate = T,
       width = 0,
       efac = .5,
       pch = 19,
       clim = c(-1,1),
       cex.lab = 1,
       cex.axis = 1,
       cex = .85,
       lty = c("solid", "solid",  "solid"),
       xlab = "",
       mlab = "Neuroticism - Emotion variability \n RE: k = 35, p = 0.044",
       showweights = F,
       steps = 5)
```

### Neuroticism and variability in Well-being

Analyses are run separately for each personality trait. For ease of presentation, only the model for Neuroticism is shown here:

```{r, fig.width = 7, fig.height = 10}
neuroticism <- rma.mv(yi = Corr,
                      V = vi,
                      data = data[which(data$Pers == "Neuroticism" & !is.na(data$WB)),],
                      method = "REML",
                      level = 95, 
                      digits = 4,
                      slab = ID,
                      random = ~1 | ID)
neuroticism

par(mar=c(2.5,4,1,2.5), cex = .9, font = 1)

forest(neuroticism,
       xlim = c(-2,2),
       order = "obs",
       addfit = T,
       annotate = T,
       width = 0,
       efac = .5,
       pch = 19,
       clim = c(-1,1),
       cex.lab = 1,
       cex.axis = 1,
       cex = .85,
       lty = c("solid", "solid",  "solid"),
       xlab = "",
       mlab = "Neuroticism - Well-being variability \n RE: k = 31, p < 0.001",
       showweights = F,
       steps = 5)
```


### Moderator: ESM vs. LD

The first moderator is the repeated-measure design. A study is considered `ESM` if it uses rapid assessments with frequency from daily to multiple times a day. Examples include experience sampling methods and daily diary studies. A study is considered `LD` if it uses traditional longitudinal design with assessments ranging from weeks, months, to years apart. For ease of presentation, only models for trait Neuroticism are tested for moderators. Because all studies with well-being are traditional longitudinal design, only models with emotional variability are tested for this moderator

```{r}
designEmo <- rma.mv(yi = Corr,
                     V = vi, 
                     mods = ~factor(Design),
                     data = data[which(data$Pers == "Neuroticism"& !is.na(data$EmoPN)),],
                     random = ~1 | ID)
designEmo
```

### Moderator: Positive vs. Negative affect

```{r}
EmoPN <- rma.mv(yi = Corr,
                V = vi, 
                mods = ~factor(EmoPN),
                data = data[which(data$Pers == "Neuroticism"& !is.na(data$EmoPN)),],
                random = ~1 | ID)
EmoPN
```